Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Added Remark 4.45

\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}
\pg{It is done in Coro~\ref{coro::exchangeablePairsNKC}.}

@@

\begin{definition}\label{defn::mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e. any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$). \pg{To simplify, we should perhaps ask for the approximations to be minimal.}\yann{added missing  ``indecomposable'' which fixes this issue}
\end{definition}

@@

\begin{lemma}
\label{lemm::then-AR-seq-are-mutation}
Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
Assume that:\yann{There might be some redundancies in the assumptions}\pg{If so, it's not obvious to me.}
\begin{enumerate}
 \item $X\notin\add(\susp\Lambda)$;
 \item $M$ and~$\tau M$ are~$\tau$-rigid;
 \item $\Hom{\Lambda}(M,\tau^2 M)=0$;
 \item $\tau M$ is a brick.
\end{enumerate}
Then~$\tau X\infl E\defl X$ is a mutation conflation.
\end{lemma}

>>>>

@@

\begin{definition}\label{defn::mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e. any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
\end{definition}
\begin{remark}
In Definition~\ref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
\end{remark}

@@

\begin{lemma}
\label{lemm::then-AR-seq-are-mutation}
Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
\begin{enumerate}
 \item $X\notin\add(\susp\Lambda)$;
 \item $M$ and~$\tau M$ are~$\tau$-rigid;
 \item $\Hom{\Lambda}(M,\tau^2 M)=0$;
 \item $\tau M$ is a brick.
\end{enumerate}
Then~$\tau X\infl E\defl X$ is a mutation conflation.
\end{lemma}
